Simulating cosmic variance in Weak Lensing: effects on parameter inferences

### 2015-12-04 Paper/paper.tex
fixed 100-->200 mislabel

\begin{figure}
\includegraphics[scale=0.3]{Figures/means_ns.eps}
\caption{Means of shear features $d$ measured from different shear ensembles. The quantities shown are the differences between mean features measured from ensemble with varying $N_s$, with respect to the means measured from the $N_s=200$ ensemble, in units of the statistical error measured from the $N_s=100$ ensemble. The colored lines refer to shear-shear power spectra measured at $l=115$ (black), 1027 (cyan), 5283 (green) and peak counts of height $\kappa_0=0.05$ (red), 0.17 (purple), 0.28 (orange).}
\label{means_ns}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.3]{Figures/means_ns.eps}
\caption{Means of shear features $d$ measured from different shear ensembles. The quantities shown are the differences between mean features measured from ensemble with varying $N_s$, with respect to the means measured from the $N_s=200$ ensemble, in units of the statistical error measured from the $N_s=200$ ensemble. The colored lines refer to shear-shear power spectra measured at $l=115$ (black), 1027 (cyan), 5283 (green) and peak counts of height $\kappa_0=0.05$ (red), 0.17 (purple), 0.28 (orange).}
\label{means_ns}
\end{figure}
